GPU-friendly Stroke Expansion

### 2024-04-18 paper.tex
First cut at CPU performance measurement
This just compares against Skia, which is not especially informative.

Skia has a bug that causes over-subdivision at fine tolerances. Our code could also be more optimized; particularly low-hanging fruit includes not evaluating the Euler spiral twice for both sides of a stroke.

The SVG parser now takes into account the scale, which is especially important for the waves example.

>>>>

We measured the timing of our CPU implementation, generating both line and arc primitives, against Skia's stroker, which outputs quadratic Bézier primitives. The results are shown in Figure~\ref{fig:timings}. The time shown is the total for test files from the \emph{timings} dataset of \cite{Nehab2020}, and the tolerance in all cases was 0.25. TODO: measure against other implementations.

\begin{figure}
    \includegraphics[scale=0.6]{timings}
    \caption{Timing for stroke expansion}
    \Description{A stacked bar chart of the timings for stroke expansion}
    \label{fig:timings}
\end{figure}

We also compared the number of primitives generated, for varying tolerance values from 1.0 to 0.001. The number of arcs generated is significantly less than the number of line primitives. The number of arcs and quadratic Bézier primitives is comparable at practical tolerances, but the count of quadratic Béziers becomes more favorable at finer tolerances. These vertical axis shows the sum of output segment counts for test files from the \emph{timings} dataset.

\begin{figure}
    \includegraphics[scale=0.6]{prim_count}
    \caption{Primitive count for stroke expansion}
    \Description{A line chart showing the primitive count}
    \label{fig:prim_count}
\end{figure}

NOTE: the increase in Skia numbers at tolerances below 0.01 or so is the result of a precision bug in Skia, uncovered during preparation of this chart. We expect that to be fixed, and will revise the chart.
